\Title

### 2021-01-28 manuscript/manuscript.tex
Small fix on writing

Our gradient boosting algorithm for overlapping windows is similar to the
``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
fits portions of an equivalent source model to the data residuals.
The key differences are that in our method:
(1) the sources in the overlapping portions of the windows are
fit more than once, allowing the algorithm to self-correct for poor solutions
to any given window;
(2) we use only data points within the window when fitting the data enables the
use of larger datasets;
(3) experience shows that the step size parameter improves the convergence of
the solution, particularly when using only the data inside the windows for
fitting.

>>>>

Our gradient boosting algorithm for overlapping windows is similar to the
``bootstrap inversion'' used in \citet{vonfrese1988}, which also iteratively
fits portions of an equivalent source model to the data residuals.
The key differences are that in our method:
(1) the sources in the overlapping portions of the windows are
fit more than once, allowing the algorithm to self-correct for poor solutions
to any given window;
(2) we use only data points within the window when fitting, what enables the
use of larger datasets;
(3) experience shows that the step size parameter improves the convergence of
the solution, particularly when using only the data inside the windows for
fitting.
